---
title: "Genetic Algorithms Notebook"
output: html_notebook
---
```{r,echo=FALSE}
library(tidyverse)
library(dplyr)
```
This notebook walks through basic genetic algorithms and tracking their performance over time. These algorithms will make up the basis of the phenotypic evolution of honeybees within the colony,so this is a good place to start.
I have written several functions in other .R files that will be utilized here.

#Introduction
##Genetic Algorithms
A genetic algorithm is a form of optimization used in computer science belonging to a larger class of evolutionary algorithms, which in general begin with a population of random inputs to a function and impose slow changes to approach a better solution. Genetic algorithms are used to optimize inputs according to some fitness function, however complex or abstract it may be. As its name implies, genetic algorithms are inspired by the process of natural selection and, specifically, some factors of genetics that allow for beneficial mutations such as crossover.

In a genetic algorithm, a population of candidate solutions (called individuals, creatures, or phenotypes) to an optimization problem is evolved toward better solutions. Each candidate solution has a set of properties (its chromosomes or genotype) which can be mutated and altered; traditionally, solutions are represented in binary as strings of 0s and 1s, but other encodings are also possible. (Wikipedia; Whitley, Darrell (1994))


#Applying Genetic Algorithm
##Creating a Species

##Creating a Population


Define function
```{r}
fitfunc <- function(x,y)
{return((x^2+y^2))}
```

#Function Running
```{r}
geneticSpecies(fitfunc,gens=100,indivs=3,creation="child")
```


```{r}
geneticPopulation(
  fitfunc,species=10,indivs=10,gens=100,creation="new",plot="time")
```
```{r}
geneticPopulation(
  fitfunc,species=10,indivs=10,gens=100,creation="child",plot="time")
```

```{r}
geneticPopulation(
  fitfunc,species=10,indivs=10,gens=100,creation="new",plot="maxVals")
```

```{r}
geneticPopulation(
  fitfunc,species=10,indivs=10,gens=100,creation="child",plot="maxVals")
```


