---
title: "Sociality Simulation"
author: Maxwell Greene
output: pdf_document
---

```{r,include=FALSE}
library(ggplot2)
library(plot3D)
library(gridExtra)
library(plotly)
library(ggenealogy)
#load(file="SocSimNBWS.RData")
figW <- 7; figH <- 3.5; figA = "center"

source('/cloud/project/Sociality Simulation/newSocSim.R', echo=FALSE)
#source('/cloud/project/Sociality Simulation/VisData.R', echo=FALSE)
```
```{r setup, include=FALSE}
library(knitr)
library(rgl)
knit_hooks$set(webgl = hook_webgl)
```



Initialize environment and colony attributes 
```{r}
env <- c(0.9,0.7,0.5,0.7)

col <- c(0.6,0.7,0.8,0.75)

ftype <- "quad"
```

Initialize parameters
```{r}
#Set number of Days in a Cycle
Day <- 0;       nDayCycle <- 100;

#Starting number of reproductives, workers and energy stores
nReprod <- 1;   nWorker <- 0;   kStore <- 0;

#Set amount of energy per day that workers and reproductives make
kWorker <- 2;   kReprod <- 2;

#Set amount of energy needed to create a worker and reproductive
cWorker <- 5;   cReprod <- 5.5;

#Combine all into a single vector
params <- c(Day,nDayCycle,nReprod,nWorker,kStore,kWorker,kReprod,cWorker,cReprod)
```


Run Single Colony, Single Season Simulation
```{r}
seasonData <- newRunSim(enviro = env,
                        colony = col,
                        params = params)
```

Visualize Single Colony, Single Season Simulation
```{r}
newVisCol(data = seasonData, 
          env = env,
          col = col,
          type = ftype)
```

Run Repeated Colony, Single Season Simulation
```{r}
repeatSeasonData <- newRunSimRep(nRun = 1000,
                                 env = env,
                                 col = col,
                                 ftype = ftype,
                                 params = params)
```

Visualize Repeated Colony, Single Season Simulation
```{r}
#VisRepHist(nReprods = repeatSeasonData,enviro = env,colony = col)
newVisDensity(nReprods = repeatSeasonData)
```

Run given environment with many different colonies
```{r}
manyColonyData <- newRunSimEnv(env   = env,
                               type  = ftype,
                               nRun  = 20,
                               nEach = 8)
```

```{r}
newVisDensity(manyColonyData$nReprod)
```

```{r}
newVisPopParamsPlotly(manyColonyData)
```

Run given colony with many different environments
```{r}
manyEnvironmentData <- newRunSimCol(col = col,
                                    type  = ftype,
                                    nRun  = 20,
                                    nEach = 8)
```

Plot density of nReprods for a given colony across many environments
```{r}
newVisDensity(manyEnvironmentData$nReprod)
```

Visualize the parameter success for a given colony across many different environments
```{r}
newVisPopParamsPlotly(manyEnvironmentData)
```


Run given environment with many different colonies and evolve
```{r}
manyColonyEvolveData <- newRunSimEnvGen(env   = env,
                                        type  = ftype,
                                        nRun  = 50,
                                        nEach = 3,
                                        nGen  = 5)
```

Plot density of nReprods for a given environment across many colonies
```{r}
newVisDensity(manyColonyEvolveData$nReprod)
```

Visualize the parameter success for a given environment across many different colonies
```{r}
newVisPopParamsPlotly(manyColonyEvolveData)
```



Run given environment with many different colonies and evolve and track lineage
```{r}
manyColonyEvolveLineageData <- newRunSimEnvGenLin(env   = env,
                                                  ftype  = ftype,
                                                  nRun  = 50,
                                                  nEach = 3,
                                                  nGen  = 5)
```

Plot density of nReprods for a given environment across many colonies evolved and tracked
```{r}
newVisDensity(manyColonyEvolveLineageData$nReprod)
```

Visualize the parameter success for a given environment across many different colonies evolved and tracked
```{r}
newVisPopParamsPlotly(manyColonyEvolveLineageData)
```

Visualize the lineage path between two colonies in an evolved population
```{r}
newVisLinPath(manyColonyEvolveLineageData,"0","80","generation","child")
```

Visualize the ancestral tree of a population, given an environment and evolved
```{r}
newVisAncTree(manyColonyEvolveLineageData,indiv = "18")
```










