---
title: "Threshold Task Performance Exploration"
output: pdf_document
---

This document will be solidly based off of a simulation originalyl created in the early 2000's by Myerscough and Oldroyd in a paper titled ["Simulation models of the role of genetic variability in social insect task allocation" ]("https://link.springer.com/content/pdf/10.1007/s00040-003-0713-1.pdf")

```{r}
library(tidyverse)
library(dplyr)
```

Let's start by creating a population:
```{r}
nSubFam <- 2
nIndiv <- 100
population <- data.frame(SubFam = rep(1:nSubFam,each=nIndiv),
                         Thresh = rep(rep(sample(0:100,nSubFam)),each=nIndiv),
                         Status = rep(0,nSubFam*nIndiv))
head(population)
```

Now, let's run these individuals through a time-series random generator.
```{r}
nGen <- 1200
nEachGen <- 1
Thresh <- c(50,20,80)
sumStatus <- 1

for(genNum in 1:nGen)
{
  temprows <- sample(1:nrow(population),nEachGen)
  population$Status[temprows] <- 
    ifelse(population$Thresh[temprows]>Thresh[ceiling(genNum/(nGen/3))],1,0)
  sumStatus[genNum] <- sum(population$Status)
}

head(population)
```

```{r}
ggplot(data=data.frame(sumStatus=sumStatus)) +
  geom_point(mapping=aes(x=1:length(sumStatus),y=sumStatus)) + 
  geom_hline(mapping=aes(yintercept=10))
```

This was a pretty simple simulation paper.






Myerscough, M. R., and B. P. Oldroyd. "Simulation models of the role of genetic variability in social insect task allocation." Insectes Sociaux 51.2 (2004): 146-152.